---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# LRO.utilities

R package: Utility functions and addins for RStudio.

Helper tools I use in many projects. 

By Ludvig R. Olsen,  
Cognitive Science, Aarhus University.  
Started in Feb. 2017  

Contact at:  
r-pkgs@ludvigolsen.dk  


Main functions:   

* polynomializer
* %ni%
* insertPipe (Addin)
* scaler, scaler_, scaler_fit, scaler_fit_, scaler_transform, scaler_invert
* binarizer, binarizer_
* rename_col
* savage_dickey

## Installation  
Development version:  

> install.packages("devtools")
>
> devtools::install_github("LudvigOlsen/LRO.utilities")  

## Use 

### Addins

* Install package.
* Add key command by going to:   
    - *Tools* > *Addins* > *Browse Addins* > *Keyboard Shortcuts*.  
    - Find **Insert %>%** and press its field under *Shortcut*. 
    - Press desired key command.
    - Press *Apply*.
    - Press *Execute*.
* Press chosen key command inside R Markdown document.  

### Examples

```{r message=FALSE, warning=FALSE}
# Attach packages
library(LRO.utilities)
library(dplyr) # %>% 
library(knitr) # kable()
```

---

#### polynomializer

Exponentiate vectors to make polynomials of degree 2 to degree.

E.g. create columns v^2, v^3, v^4...

```{r}
# On vector

vect <- c(1,3,5,7,8)

polynomializer(vect, degree = 3) %>% 
  kable()

# On vectors in dataframe

data <- data.frame(vect = vect,
                   bect = vect*3,
                   dect = vect*5)

polynomializer(data, 
               cols = c('bect','dect'), 
               degree = 3) %>% 
  kable()
```

---

#### %ni%

"Not in"

```{r}

c(1,3,5) %ni% c(2,3,6)

```

---

#### scaler

Center and/or scale multiple columns of a dataframe.

**scaler** is designed to work with %>% pipelines.

**scaler_fit** returns fit_object with information used to transform data.

**scaler_transform** scales data based on the information in the fit_object.

**scaler_invert** inverts scaling based on the information in the fit_object.

**scaler_** and **scaler_fit_** are standard evalution versions.  

```{r}

# Scale and center 'vect' and 'bect' 
# in dataframe from previous example
scaler(data, vect, bect) %>% 
  kable()

# Only scaling 'vect'  - working in pipeline
data %>% 
  scaler(vect, center = F) %>% 
  kable()

# Only center 'bect' and 'dect' 
# selecting with column index range
data %>% 
  scaler(2:3, scale = F) %>% 
  kable()

```

##### Fit / Transform / Invert

```{r}
# Fit scaler
fitted_scaler <- data %>% 
  scaler_fit()

fitted_scaler %>% kable()

# Transform data
scaled_df <- data %>% 
  scaler_transform(fit_object = fitted_scaler)

scaled_df %>% kable()

# Invert scaling
scaled_df %>% 
  scaler_invert(fit_object = fitted_scaler) %>% 
  kable()

```

---

#### binarizer

Binarize multiple columns of a dataframe based on a given threshold.

**binarizer** is designed to work with %>% pipelines.

**binarizer_** is a standard evalution version.

```{r}

scaled_df %>% 
  binarizer(thresh = 0)

```


---

#### rename_col

Rename single column in dataframe. This is a bit like plyr::rename just only for 1 column at a time.

```{r}
rename_col(data, 
           old_name = 'bect', 
           new_name = 'sect') %>% 
  kable()

```


#### savage_dickey

Calculate Bayes factor from 2 distributions and (optionally) plot the the two distributions. 
Returns list with ggplot2 object, BF10, and BF01.  

```{r}
prior <- rnorm(1000, mean=0, sd=1)
posterior <- rnorm(1000, mean=2, sd=2)

s_d <- savage_dickey(posterior, prior, Q = 0, plot = TRUE)

str(s_d, max.level = 1)

s_d

```

